---
title: "p8105_hw5_cl4469"
author: "Chen Liang"
date: "2023-11-12"
output: github_document
---

```{r}
library(tidyverse)
library(patchwork)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "95%"
)

theme_set(theme_minimal() + theme(legend.position = 'bottom'))

options(
  ggplot2.continuous.colour = 'viridis',
  ggplot2.continuous.fill = 'viridis'
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1
```{r, load data}
homicide_df = read.csv("data/homicide-data.csv")
```
This dataset contains `r nrow(homicide_df)` rows and `r ncol(homicide_df)` columns, with each row resprenting a single event occurred. Variables include id, reported-date, victims'last name,race, and sex. It contains the location of the killing (city, state, latitude, longitude) and whether an arrest was made. Moreover, there are some missing values in `lat` and `lon` columns and unknown information in `victim_last`,`victim_first`,`victim_age`,`victim_sex`, and `victim_race`.

```{r}
hom_summary = homicide_df|>
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )) |>
  group_by(city_state) |>
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved"),
    home_solved = sum(resolved == "solved")
  )

hom_summary
```


